\chapter{Introduction: Go learn Lisp}

\quote{Go learn Lisp.  I hear people who know everything really like Lisp.}
--Zed Shaw

Well, I certainly don't know everything and - wait a second ... that remark was clearly fascetious! Oh well. This book will try to do that - a little. Make you learn Lisp, that is. And by "you" I mean "me". And by Lisp, I mean Clojure.

This simple book is meant to get you started in the Lisp world. I mildly suggest you start off by reading completely "Learn Python the Hard Way" and/or "Learn C the Hard Way" too. This book will assume you have at least completed ex0 of one of these (and if possible more as I will move swiftly). Going through one of these other books will give you invaluable perspective as you progress through this book. 
The title says it's the hard way to learn to write Lisp-ish code; but that's really because we will be following the same structure as the "Learn X the Hard Way" series. To reiterate what that approach is all about, here is what you will do:

\begin{enumerate}
\item Go through each exercise.
\item Type in each sample {\em exactly}.
\item Make it run.
\end{enumerate}

That's it.  

It might turn out hard, but as always stick to it.

This book doesn't pretend that it will teach you life changing things. What it hopes to do is teach you perspective and a little Lisp for your own good.

{\Large Perspective}

The one thing that separates close-minded individuals and open-minded ones is perspective. If you are reading this then chances are you want to discover what the above snarky comment by Zed Shaw was all about. Well, me too. Without being too preachy-preachy, you will find in life that there are things you can't do anything about. But the one thing you can always do is change your outlook on them. That's what the seemingly obscure Lisp world will bring you. A little bigger picture of the world of programming languages.

Beware though. Once you start on this road you will see a lot of debate -and let's be frank- religious wars over programming languages. Numerous pundits will tell you Lisp is the best thing ever, while equally numerous pundits will villify it and belittle it. Ignore both sides. As far as you are concerned right now, Lisp is another language period.

With that in mind let's go learn (the hard way) Lisp (Clojure)! 